### 2019-07-12 README.Rmd
Update README

In functions throughout the `hurricaneexposure` package, storms are identified based on their name and year (e.g., Hurricane Floyd in 1999 is identified as "Floyd-1999"). Note that a few storms satisfied the criteria to be included in the data but were unnamed (e.g., "Notnamed" in 1991, "Subtrop" in 1997, etc.). These storms are identified in functions in the `hurricaneexposure` package based on the identifying name listed in the above table (e.g., "Notnamed-1991"), although for some research projects you may want to consider excluding these unnamed storms from the analysis.

@@

```{r warning = FALSE}
communities <- data.frame(commun = c(rep("ny", 6), "no", "new"),
                         fips = c("36005", "36047", "36061",
                                  "36085", "36081", "36119",
                                  "22071", "51700"))
multi_county_rain(communities = communities, start_year = 1995, end_year = 2005,
                   rain_limit = 100, dist_limit = 100)
```

>>>>

In functions throughout the `hurricaneexposure` package, storms are identified based on their name and year (e.g., Hurricane Floyd in 1999 is identified as "Floyd-1999"). Note that a few storms satisfied the criteria to be included in the data but were unnamed (e.g., "Notnamed" in 1991, "Subtrop" in 1997, etc.). These storms are identified in functions in the `hurricaneexposure` package based on the identifying name listed in the above table (e.g., "Notnamed-1991", "Td08-2016"), although for some research projects you may want to consider excluding these unnamed storms from the analysis.

@@

```{r warning = FALSE}
communities <- data.frame(community_name = c(rep("ny", 6), "no", "new"),
                         fips = c("36005", "36047", "36061",
                                  "36085", "36081", "36119",
                                  "22071", "51700"))
multi_county_rain(communities = communities, start_year = 1995, end_year = 2005,
                   rain_limit = 100, dist_limit = 100)
```
